linearGR_Models

### 2018-06-22 manuscriptAnalysis/MS_Analysis.Rmd
updated mcmcInfo

>>>>

```{r bnt density}

ggplot(d2, aes(cBNTStd)) +
  geom_histogram() +
  facet_grid(season~riverOrdered)

ggplot(d2, aes(cBNTStd, grLength)) +
  geom_point(alpha=0.1) +
  geom_smooth(method='lm') +
  facet_grid(isYOY+season~riverOrdered)

ggplot(d2, aes(cBKTStd, grLength)) +
  geom_point(alpha=0.1) +
  geom_smooth(method='lm') +
  facet_grid(isYOY+season~riverOrdered)
```

### 2018-06-22 manuscriptAnalysis/linearGR_ModelsMap_BKT.Rmd
updated mcmcInfo

>>>>

> bySpecies$model18[[2]]
Linear mixed model fit by REML ['lmerMod']
Formula: grLength ~ isYOY * river * season * tempStd * flowStd + isYOY *  
    river * season * cBKTStd + isYOY * river * season * cBNTStd +  
    isYOY * season * cATSStd + isYOY * river * season * cBNTStd2 +  
    isYOY * river * season * cBNTStd * cBKTStd + (1 | ind) +      (1 | season)
   Data: df
REML criterion at convergence: -11461.98
Random effects:
 Groups   Name        Std.Dev.
 ind      (Intercept) 0.01955 
 season   (Intercept) 0.08491 
 Residual             0.06018 
Number of obs: 4495, groups:  ind, 2714; season, 4

> bySpecies$model11[[3]]
Linear mixed model fit by REML ['lmerMod']
Formula: grLength ~ isYOY * river * season * tempStd * flowStd + isYOY *  
    season * cBKTStd * cBNTStd * cATSStd + (1 | ind) + (1 | season)
   Data: df
REML criterion at convergence: -29539.29
Random effects:
 Groups   Name        Std.Dev.
 ind      (Intercept) 0.01831 
 season   (Intercept) 0.03268 
 Residual             0.03954 
Number of obs: 8732, groups:  ind, 4183; season, 4
